SEER Medicaid

### 2023-10-04 Manuscript Analysis code 0 to 19.Rmd
edited some code that resulted in incorrect Supplementary Table 2 output to excel

SuppTable2$`Survival Percentage (95% CI)` <-paste0(SuppTable2$`Survival Percentage`, " (", SuppTable2$`lower 95% CI`, " to ", SuppTable2$`upper 95% CI`, ")")
# drop uneeded columns
SuppTable2 <- SuppTable2 %>%
  dplyr::select(1,5)

>>>>

SuppTable2$`Survival Percentage (95% CI)` <-paste0(SuppTable2$`Survival Percentage`, " (", SuppTable2$`lower 95% CI`, " to ", SuppTable2$`upper 95% CI`, ")")
# drop uneeded columns
SuppTable2 <- SuppTable2 %>%
  dplyr::select(1,6)
